Tidy data structure to support exploration and modeling of temporal-context data

### 2018-11-09 main.Rmd
updated data

The choice of representation of temporal-context data is made from a data-centric perspective, which is taken in the light of the operations that are to be performed on the data. This data abstraction reflects most common problems of incoming data and transformation in reality. Firstly, a data set must be structured in a "tidy" rectangular layout each row has the same schema and each field has a single value. Secondly, declaring the data set to contain temporal observations is determined by an "index" that represents time and a "key" that uniquely identifies each unit that measurements take place on over time. The "key" serves a similar purpose as the panel variable in the Stata's **tsset** command to define the units or subjects, but it is expanded to include multiple variables rather than a single one. The composition of index and key uniquely defines each observation in a data table, which is equivalent to a primary key [@codd_relational_1970] in a relational database. (The matrix representation also implies that every observation is determined by column variable and time-indexed row.)

@@

Time forms an integral component and a contextual basis of temporal data. A variable representing time needs explicitly declared at the process of constructing a temporal data, referred to as "index". This accessibility of index promotes transparency and unambiguity while manipulating time. For example, subsetting a certain time period of data, extracting time components (like time of day and day of week), or converting time zones are directly dealt with index. It is also often to join other data tables based on the common time indices. Tools are provided to work with time itself, rather than wrappers to work with a whole data set. This promotes transparency and visibility to make inspection easier. This sets the tone on methods design philosophy: well-structured, expressive and unambiguous workflow.

>>>>

The choice of representation of temporal-context data is made from a data-centric perspective, which is taken in the light of the operations that are to be performed on the data. This data abstraction reflects most common problems of incoming data and transformation in reality. Firstly, a data set must be structured in a "tidy" rectangular layout each row has the same schema and each field has a single value. Secondly, declaring the data set to contain temporal observations is determined by an "index" that represents time and a "key" that uniquely identifies each unit that measurements take place on over time. The "key" serves a similar purpose as the panel variable in the Stata's **tsset** command to define the units or subjects, but it is expanded to include multiple variables rather than a single one. The composition of index and key uniquely defines each observation in a data table, which is equivalent to a primary key [@codd_relational_1970] in a relational database.

@@

Time provides a contextual basis for temporal data. The time could range from date-times (such as `POSIXct` and `Date` in R) to year-months, to years.

A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact column instead of an attribute. This accessibility of index promotes transparency and unambiguity while manipulating time. For example, subsetting a certain time period of data, extracting time components (like time of day and day of week), or converting time zones are directly dealt with index. It is also often to join other data tables based on the common time indices. Tools are provided to work with time itself, rather than wrappers to work with a whole data set. This promotes transparency and visibility to make inspection easier. This sets the tone on methods design philosophy: well-structured, expressive and unambiguous workflow.
